Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
art description

To simulate sequencing error in the sequence of interest,
 we use the the next-generation sequencing read simulator 
ART~\cite{huang2012art}. The Illumina technology main error mode is base substitution. We used
this model since those
are the errors that \RNApyro detects. As parameters, the reads  generated
were $75\text{bps}$ long for an average fold coverage of $5$, $10$ and $15$. 
 They yield respectively an average error rate of $2.4\%$, $0.9\%$ and $0.6\%$.

We used a value of $\beta=15$ and evaluated $\alpha$ at $0, 0.5, 0.8, 1.0$. 
 Additionally since the alignment still contains gap, we made sure to evaluate the isostericity 
 term only
 with sequences in the MSA where both positions in the base pair are not gaps. 
 Due to the low number of errors, we set the presumed as twice the average error rate made by ART, i.e. $4.8\%$, $1.8\%$ and $1.2\%$ for fold coverages of $5$, $10$ and $15$ respectively.

@@

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-b}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-b}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-b}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction over positions inside a base pair. Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}
\label{fig:16s_bp}
\end{figure}

>>>>

To simulate sequencing error in the sequence of interest,
 we use the the next-generation sequencing read simulator 
\ART~\cite{huang2012art}. The Illumina technology main error mode is base substitution. We used
this model since those
are the errors that \RNApyro detects. As parameters, the reads  generated
were $75\text{bps}$ long for an average fold coverage of $5$, $10$ and $15$. 
 They yield respectively an average error rate of $2.4\%$, $0.9\%$ and $0.6\%$. \ART reads
 are automatically mapped to the sequence of interest. For every position covered by reads, 
 we selected the nucleotide appearing more frequently. At un-covered position, we picked a random
 nucleotide.

We used a value of $\beta=15$ and evaluated $\alpha$ at $0, 0.5, 0.8, 1.0$. 
 Additionally since the alignment still contains gap, we made sure to evaluate the isostericity 
 term only
 with sequences in the MSA where both positions in the base pair are not gaps. 
 Due to the low number of errors, we set the presumed as twice the average error rate made by \ART, i.e. $4.8\%$, $1.8\%$ and $1.2\%$ for fold coverages of $5$, $10$ and $15$ respectively. \ART reads

@@

 \begin{figure}
\centering
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/5fold-b}
  \caption{$5-$fold coverage}
\end{subfigure}%
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/10fold-b}
    \caption{$10-$fold coverage}
\end{subfigure}
\begin{subfigure}{.33\textwidth}
  \centering
  \includegraphics[width=\linewidth]{figures/15fold-b}
    \caption{$15-$fold coverage}
\end{subfigure}
\caption{Performance of error-correction over structured positions (i.e. inside a base pair). Subfigures show accuracy when
ART fold parameter is set to 5, 10 and $15-$fold coverage. We also analyze the impact of the parameter $\alpha$ distributing the weights of stacking pair energies vs isostericity scores and use values ranging of $\alpha = \{0, 0.5, 0.8, 1.0\}$. The AUC is indicated in the legend of the figures. Each individual ROC curve represent the average performance over at least 10 experiments.}
\label{fig:16s_bp}
\end{figure}
